Colorimetric Detection of pH Strips

### 2017-12-10 CS189/paper/paper.tex
preliminary paper completed
fix figures layout

% Template Acknowledgements:
%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
\documentclass[journal]{IEEEtran}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}
\graphicspath{{../figures/}}

@@

\begin{figure}
\centering
\includegraphics[height=2.5in]{pca.png}
\caption{Raw color extracted data projected onto two orthogonal axes such that variance captured is maximized.}
\label{pca}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{SVM/svm_classification.png}
\caption{Support Vector Machine Classification Model. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is the regularization strength. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{svm}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2.5in]{SVM/SVM_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for SVM model. The confusion matrix plots the predicted class on the X axis, and the true class on the Y axis. Therefore, elements along the diagonal of the matrix were predicted correctly. In this case, 2 of 27 images were misclassified.}
\label{svm_confusion}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{LDA/lda_classification.png}
\caption{Linear Discriminant Analysis Classification Model. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is different number of components we project the data onto when doing PCA. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{lda}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2.5in]{LDA/LDA_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for LDA model. None of the images were misclassified in this fold.}
\label{lda_confusion}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{KNN_clf_noPCA/knn_classification.png}
\caption{K Nearest Neighbor Classification Model. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is the number of neighbors used in the model. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{knn}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2.5in]{KNN_clf_noPCA/KNN_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for kNN model (without PCA/scaling). 2 of 35 images were misclassified.}
\label{knn_confusion}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{KNN_clf_PCA/knn_classification.png}
\caption{K Nearest Neighbor Classification Model, with PCA and scaling preprocessing. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is the number of neighbors used in the model. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{knn_pca}
\end{figure}

@@

@@

\begin{figure}
\centering
\includegraphics[height=2in]{KNN_reg_noPCA/knn_regression.png}
\caption{TODO.}
\label{Rknn}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{KNN_clf_PCA/knn_classification.png}
\caption{TODO.}
\label{Rknn_pca}
\end{figure}

@@

\subsection{Acknowledging our Shortcomings}
While both this experiment and the Mutlu experiment used 90 pH test strips in the creation of the training dataset, both experiments should be repeated with much larger training sets for more reliable results. Given additional resources, an increased training set may have allowed for further improvements in training and test accuracy. A larger training set may have also helped both the regression and classification models become more robust with respect to noise, including lighting changes and color correction. More training data would also help reduce variance across the results of several models.

@@

\section{Conclusion}
Overall, we were able to develop both classification and regression models in this domain and obtain relatively high accuracy and low error. In spite of our similarly-sized dataset including more varied data for each pH value tested, we were able to match the classification accuracy ($100\%$) achieved by Mutlu while mimicking the various lighting changes in the data. We were also able to extend Mutlu’s findings using regression techniques, and successfully achieved low error in doing so.

>>>>

% Template Acknowledgements:
%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
\documentclass[journal]{IEEEtran}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}
\usepackage{textcomp}
\graphicspath{{../figures/}}

@@

\subsection{Pre-Processing}
\begin{figure}
\centering
\includegraphics[height=2.5in]{pca.png}
\caption{Raw color extracted data projected onto two orthogonal axes such that variance captured is maximized.}
\label{pca}
\end{figure}

@@

\subsection{Classification Models}

\begin{figure}
\centering
\includegraphics[height=2in]{SVM/svm_classification.png}
\caption{Support Vector Machine Classification Model. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is the regularization strength. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{svm}

\centering
\includegraphics[height=2.5in]{SVM/SVM_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for SVM model. The confusion matrix plots the predicted class on the X axis, and the true class on the Y axis. Therefore, elements along the diagonal of the matrix were predicted correctly. In this case, 2 of 27 images were misclassified.}
\label{svm_confusion}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{LDA/lda_classification.png}
\caption{Linear Discriminant Analysis Classification Model. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is different number of components we project the data onto when doing PCA. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{lda}

\centering
\includegraphics[height=2.5in]{LDA/LDA_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for LDA model. None of the images were misclassified in this fold.}
\label{lda_confusion}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{KNN_clf_noPCA/knn_classification.png}
\caption{K Nearest Neighbor Classification Model. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is the number of neighbors used in the model. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{knn}

\centering
\includegraphics[height=2.5in]{KNN_clf_noPCA/KNN_classification_cfm.png}
\caption{Sample confusion matrix for one fold of $k=3$ cross validation for kNN model (without PCA/scaling). 2 of 35 images were misclassified.}
\label{knn_confusion}

\centering
\includegraphics[height=2in]{KNN_clf_PCA/knn_classification.png}
\caption{K Nearest Neighbor Classification Model, with PCA and scaling preprocessing. The Y axis is the Accuracy (percent of predicted labels that are correct) and the X axis is the number of neighbors used in the model. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{knn_pca}
\end{figure}

@@

\subsection{Regression Models}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{KNN_reg_noPCA/knn_regression.png}
\caption{K Nearest Neighbor Regression Model. The Y axis is the Mean Squared Error and the X axis is the number of neighbors used in the model. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{Rknn}

\centering
\includegraphics[height=2in]{KNN_clf_PCA/knn_classification.png}
\caption{K Nearest Neighbor Regression Model, with PCA and scaling preprocessing. The Y axis is the Mean Squared Error and the X axis is the number of neighbors used in the model. The four lines represent the four datasets we used: no color change, with gamma modification, with color rotation, and with both gamma modification and color rotation.}
\label{Rknn_pca}
\end{figure}

@@

\subsection{Acknowledging Shortcomings}
While both this experiment and the Mutlu experiment used 90 pH test strips in the creation of the training dataset, both experiments should be repeated with much larger training sets for more reliable results. Given additional resources, an increased training set may have allowed for further improvements in training and test accuracy. A larger training set may have also helped both the regression and classification models become more robust with respect to noise, including lighting changes and color correction. More training data would also help reduce variance across the results of several models.

@@

\section{Conclusion}
Overall, we were able to develop both classification and regression models in this domain and obtain relatively high accuracy and low error. In spite of our similarly-sized dataset including more varied data for each pH value tested, we were able to match the classification accuracy ($100\%$) achieved by Mutlu while mimicking the various lighting changes in the data. We were also able to extend Mutlu\textquotesingle s findings using regression techniques, and successfully achieved low error in doing so.
